---
title: "Final Project R Code"
author: "Chrislin, Dhivya, Rajeshwari, Varun"
date: "April 13, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r }
library(knitr,warn.conflicts = F)
library(foreign,warn.conflicts = F)
library(ggplot2,warn.conflicts = F)
library(tidyr,warn.conflicts = F)
library(plyr, warn.conflicts = F)
library(viridis, warn.conflicts = F)
library(dplyr, warn.conflicts = F)
```


# Initial filtering of dataset to "final_dataset.csv" using the aggregate and kills data:

```{r}
#agg_0<-read.csv("Downloads/pubg-match-deaths/aggregate/agg_match_stats_0.csv",header = T,stringsAsFactors = F)
#kills_0<-read.csv("Downloads/pubg-match-deaths/deaths/kill_match_stats_final_0.csv",header = T,stringsAsFactors = F)

#kills_0 <- kills_0 %>% filter(map == "MIRAMAR")

#final_dataset <- merge(kills_0,agg_0,by.x = c("match_id","killer_name"),by.y = c("match_id","player_name"))

#write.csv(final_dataset,"final_dataset.csv",row.names = F)
```

```{r}
data <- read.csv("sample_dataset.csv",header = T,stringsAsFactors = F)
#View(data)
```

```{r}
data <- data %>% filter(party_size == 1)
data$killed_by <- tolower(data$killed_by)
```

```{r}
data=data[!is.na(data$killer_placement),]
nrow(data)
```

#Code used to take a sample of the final dataset:

```{r}
#complete_data <- data
#data.matches <- unique(data$match_id)
#data.matches <- data.matches[1:500]
#data <- data %>% filter(match_id %in% data.matches)
#write.csv(data,"sample_dataset.csv",row.names = F)
```

```{r}
ggplot(data,aes(x=time))+geom_histogram(position='dodge',bins=20,fill='darkblue')+
        xlab("Time into the game (seconds)")+
        ylab("Number of kills")+
        labs(title="Number of kills against time")+
        scale_x_continuous(breaks=seq(0,3000,200))+
        theme_bw()+
        theme(plot.title = element_text(hjust = 0.5),
              axis.title.y = element_text(),
              axis.title.x = element_text(),
              axis.text.x = element_text(),
              axis.text.y = element_text())+
        theme(panel.border = element_rect(colour = "black", fill = NA))+
        theme(panel.background = element_rect(fill = "white"))
```


```{r}
library(dplyr)
kill_data<-data
kill_data$kill_distance<-((kill_data$killer_position_x - kill_data$victim_position_x)**2 + (kill_data$killer_position_y - kill_data$victim_position_y)**2)**(1/2)

kill_data<-kill_data%>%
                      mutate(kn = as.character(killer_name), vn = as.character(victim_name)) %>%
                                filter(kn!=vn)
grp_kill_data<-ddply(kill_data,c('killed_by'),summarise,mean_kill_distance=mean(kill_distance,na.rm = T))

grp_kill_data=grp_kill_data[!is.na(grp_kill_data$mean_kill_distance),]
grp_kill_data$killed_by2<-factor(grp_kill_data$killed_by, levels = grp_kill_data[order(grp_kill_data$mean_kill_distance),]$killed_by)

paste("no of weapons:",nrow(grp_kill_data))
```

```{r}
TOPweapon<-data.frame(killed_by=c("m416","scar-l","m16a4","akm","ump9","s1897","kar98k","sks","mini 14","s686"))
TOPweapon$isTop10<-rep('Top10',length(TOPweapon))
merge_weapon<-merge(grp_kill_data,TOPweapon,by=c("killed_by"),all.x=T)
merge_weapon[is.na(merge_weapon)]<-'Other'
```

```{r fig.width=9,fig.height=7}
ggplot(merge_weapon,aes(x=mean_kill_distance,y=killed_by2,color="orange"))+geom_point(size=3)+
        xlab("Distance between killer and victim")+
        ylab("Weapon used by the killer")+
        labs(title="Distance between killer and victim for different weapons")+
        theme_bw()+
        theme(plot.title = element_text(face='bold',hjust = 0.5, size=20),
              axis.title.y = element_text(face="bold",  size=16),
              axis.title.x = element_text(face="bold",  size=16),
              axis.text.x = element_text(size =11),
              axis.text.y = element_text(size = 11)) +
        theme(legend.title = element_text( size=14, face="bold"),
              legend.text = element_text( size = 14, face = "bold"))+
        theme(panel.border = element_rect(colour = "black", fill = NA))+
        theme(legend.position = "none") +
        theme(panel.background = element_rect(fill = "white"))
```

#Coordinates:

```{r}
distance_data = data %>% select(match_id, killer_name, victim_name, killer_position_x,killer_position_y,victim_position_x,victim_position_y)
summary(distance_data$killer_position_x)
summary(distance_data$killer_position_y)
```

#Killer:

```{r}
distance_data$norm_killer_x <- distance_data$killer_position_x * 1000/800000
distance_data$norm_killer_y <- distance_data$killer_position_y * 1000/800000
distance_data$norm_victim_x <- distance_data$victim_position_x * 1000/800000
distance_data$norm_victim_y <- distance_data$victim_position_y * 1000/800000
```

```{r}
library(jpeg)
my_image=readJPEG("miramar.jpg")
library(grid)
img = rasterGrob(my_image, width = unit(1,"npc"), height = unit(1,"npc"))
```

#All Deaths on Miramar Map
#Please note: The value of alpha has been regulated when there are more data points to depict the death hotspots in the map

```{r}
gg = ggplot(distance_data,aes(x=norm_victim_x, y=norm_victim_y)) + annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) + geom_point(size = 0.001, color = "red", alpha = 0.25) 
gg + xlim(0,1000) + ylim(1000,0) + xlab("Victim's x coordinate position") + ylab("Victim's y coordinate position") + ggtitle("Death hotspots in the game on the Miramar map") + theme(plot.title = element_text(hjust = 0.5))
```


```{r}
weapon_data = data %>% select(match_id, killer_name, victim_name, killed_by,player_kills)
weapon_data <- weapon_data %>% filter(killer_name!=victim_name)
```

```{r}
library(ggplot2)
library(dplyr)
weapon_agg <- weapon_data %>% group_by(killed_by) %>% summarise(count = n()) %>% arrange(desc(count))
```

```{r}
#summary(weapon_agg$count)
```

```{r}

weapon_agg$weapon = weapon_agg$killed_by
weapon_agg$weapon[weapon_agg$count < median(weapon_agg$count)] <- "Others"
weapon_agg2 <- weapon_agg %>% group_by(weapon) %>% summarise(count = sum(count)) %>% arrange(desc(count))
o = order(weapon_agg2$count, decreasing = F)
weapon_agg2$weapon = factor(weapon_agg2$weapon, levels = weapon_agg2$weapon[o])
ggplot(weapon_agg2,aes(x=weapon,y=count))+geom_bar(stat="identity")+coord_flip()+ theme_bw() + ggtitle("Top Lethal Weapons") + ylab("Number of Kills") + xlab("Weapon") + theme(plot.title = element_text(hjust = 0.5))
```

## change to number of kills / number of matches for each weapon
```{r}
weapon_agg_new <- weapon_data %>% group_by(killed_by,match_id) %>% summarise(count = n()) %>% arrange(desc(count))
weapon_agg_new <- weapon_agg_new %>% group_by(killed_by) %>% summarise(count = n()) %>% arrange(desc(count))

```

```{r}
colnames(weapon_agg_new)[colnames(weapon_agg_new)=="count"] <- "num_matches"
weapon_final <- merge(weapon_agg,weapon_agg_new,by=c("killed_by","killed_by"))
weapon_final$avg_kills = weapon_final$count/weapon_final$num_matches
#normalize
weapon_final$weapon_score <- weapon_final$avg_kills/sum(weapon_final$avg_kills)
summary(weapon_final$weapon_score)
```

```{r}
weapon_final3 = weapon_final %>% filter(weapon_score > 0.02300)
o = order(weapon_final3$weapon_score, decreasing = F)
weapon_final3$killed_by = factor(weapon_final3$killed_by, levels = weapon_final3$killed_by[o])

ggplot(weapon_final3,aes(x=killed_by,y = weapon_score)) + geom_bar(stat="identity", fill = colorRampPalette(c("#00BFC4"))(11)) + coord_flip() + ylab("Weapon Score") + xlab("Weapon") +  ggtitle("Ten Most Lethal Weapons") + theme(plot.title = element_text(hjust = 0.5), panel.background = element_blank()) +
geom_text(aes(label=round(weapon_score,3)), position=position_dodge(width=0.9), vjust=0.25, hjust=1.1)
```

Outlier treatment: As distance between killer and victim for punch cannot be that high

```{r}
library(plyr)
kill_data<-kill_data%>%filter(killer_position_x !=0 & killer_position_y !=0  )
kill_data<-kill_data%>%filter(victim_position_x !=0 & victim_position_y !=0  )
print(nrow(kill_data))
grp_kill_data<-ddply(kill_data,c('killed_by'),summarise,mean_kill_distance=mean(kill_distance))
grp_kill_data$killed_by2<-factor(grp_kill_data$killed_by, levels = grp_kill_data[order(grp_kill_data$mean_kill_distance),]$killed_by)
grp_kill_data<-grp_kill_data%>%mutate(isTop10=case_when(killed_by%in%c("m416","scar-l","m16a4","akm","ump9","s1897","kar98k","sks","mini 14","s686") ~ 'Top10', TRUE ~ 'Other'))
```

```{r fig.width=10,fig.height=8}
ggplot(grp_kill_data,aes(x=mean_kill_distance,y=killed_by2,color=isTop10))+geom_point(size=3)+
        xlab("Average distance between killer and victim")+
          ylab("Weapon used by the killer")+
        labs(title="Average distance between killer and victim for different weapons")+
        theme_bw()+
        theme(plot.title = element_text(face='bold',hjust = 0.5, size=18),
              axis.title.y = element_text(face="bold",  size=14,hjust = 0.6),
              axis.title.x = element_text(face="bold",  size=14),
              axis.text.x = element_text(size =12),
              axis.text.y = element_text(size = 12))+
        theme(legend.title = element_text( size=14, face="bold"),
              legend.text = element_text( size = 14, face = "bold"))+
        theme(panel.border = element_rect(colour = "black", fill = NA))+
        theme(legend.box.background = element_rect(colour = "black"))+
        theme(panel.background = element_rect(fill = "white")) + labs(color='Top 10 Weapon Flag') 
```

#Deaths by M416 Rifle on Miramar Map

```{r}
distance_data_m416 <- data %>% filter(killed_by == "m416") 
distance_data_m416$norm_killer_x <- distance_data_m416$killer_position_x * 1000/800000
distance_data_m416$norm_killer_y <- distance_data_m416$killer_position_y * 1000/800000
distance_data_m416$norm_victim_x <- distance_data_m416$victim_position_x * 1000/800000
distance_data_m416$norm_victim_y <- distance_data_m416$victim_position_y * 1000/800000
```

```{r}
library(png)
gg = ggplot(distance_data_m416,aes(x=norm_victim_x, y=norm_victim_y)) + annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) + geom_point(size = 0.001, color = "green",alpha = 0.5) 
gg + xlim(0,1000) + ylim(1000,0) + xlab("Victim's x coordinate position") + ylab("Victim's y coordinate position") + ggtitle("Death by an M416 rifle in the game on the Miramar map") + theme(plot.title = element_text(hjust = 0.5))
```


```{r}
data2 <- data
data2$killed_by <- ifelse(data2$killed_by == "motorbike (sidecar)","motorbike",data2$killed_by)
data2$killed_by <- ifelse(data2$killed_by == "death.projmolotov_damagefield_c","bluecircle",data2$killed_by)
```

```{r}
weapon_no_kills = data2 %>% select(match_id, killer_name, victim_name, killed_by,player_kills)
weapon_no_kills <- weapon_no_kills %>% filter(killer_name==victim_name)
weapon_no_kills_agg <- weapon_no_kills %>% group_by(killed_by) %>% summarise(count = n()) %>% arrange(desc(count))
weapon_no_kills_agg_new <- weapon_no_kills %>% group_by(killed_by,match_id) %>% summarise(count = n()) %>% arrange(desc(count))
weapon_no_kills_agg_new <- weapon_no_kills_agg_new %>% group_by(killed_by) %>% summarise(count = n()) %>% arrange(desc(count))
colnames(weapon_no_kills_agg_new)[colnames(weapon_no_kills_agg_new)=="count"] <- "num_matches"
weapon_final_no_kills <- merge(weapon_no_kills_agg,weapon_no_kills_agg_new,by=c("killed_by","killed_by"))
weapon_final_no_kills$avg_use_match = weapon_final_no_kills$count/weapon_final_no_kills$num_matches
#summary(weapon_final_no_kills$avg_use_match)
o = order(weapon_final_no_kills$avg_use_match, decreasing = F)

weapon_final_no_kills$killed_by = factor(weapon_final_no_kills$killed_by, levels = weapon_final_no_kills$killed_by [o])
weapon_final_no_kills <- weapon_final_no_kills %>% filter(avg_use_match>1)

ggplot(weapon_final_no_kills,aes(x=killed_by,y=avg_use_match))+geom_bar(stat="identity", fill = colorRampPalette(c("#F8766D"))(3))+coord_flip()+

theme(plot.title = element_text(hjust = 0.5), panel.background = element_blank()) +
geom_text(aes(label=round(avg_use_match,3)), position=position_dodge(width=0.9), vjust=0.25, hjust=1.1) + ggtitle("Top Reasons for Accidental Self Kills") + xlab("Manner of Death") + ylab("Average number of self kills per match")

```

#Accidentally hit by car on Miramar Map

```{r}
distance_data_car <- data %>% filter(killed_by == "hit by car") 
distance_data_car$norm_killer_x <- distance_data_car$killer_position_x * 1000/800000
distance_data_car$norm_killer_y <- distance_data_car$killer_position_y * 1000/800000
distance_data_car$norm_victim_x <- distance_data_car$victim_position_x * 1000/800000
distance_data_car$norm_victim_y <- distance_data_car$victim_position_y * 1000/800000
```

```{r}
library(png)
gg = ggplot(distance_data_car,aes(x=norm_victim_x, y=norm_victim_y)) + annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) + geom_point(size = 0.001, color = "gold", alpha = 0.5) 
gg + xlim(0,1000) + ylim(1000,0) + xlab("Victim's x coordinate position") + ylab("Victim's y coordinate position") + ggtitle("Hotspots where the victim was accidently hit by a car on the Miramar map") + theme(plot.title = element_text(hjust = 0.5))
```

## train test split

```{r}
print(length(unique(data$match_id)))
mids <- unique(data$match_id)
```
# split to make sure match ids are exclusive
```{r}
train_mid =  mids[0:400]
test_mid = mids[401:500]
```

```{r}
library(dplyr)
train <- data %>% filter(match_id %in% train_mid)
test <- data %>% filter(match_id %in% test_mid)
```

```{r}
#write.csv(train, "train.csv")
#write.csv(test, "test.csv")
```

## prediction code
## Getting required variables in train . Level of data: match id, killer name
```{r}
library(dplyr, warn.conflicts = F)
#train <- read.csv("train.csv",header = T,stringsAsFactors = F)
train = train %>% select(match_id, killer_name, player_assists, player_dist_ride,player_dist_walk,player_dmg,player_kills,player_survive_time,killer_placement)

# defining response variable
train$top10_or_not <- ifelse(train$killer_placement>10, 0, 1)
# unique for match id, killer name
train = unique(train)


train = train %>% select(player_assists, player_dist_ride,player_dist_walk,player_dmg,player_kills,player_survive_time,top10_or_not)
```


## Getting required variables in test . Level of data: match id, killer name
```{r}
#test <- read.csv("test.csv",header = T,stringsAsFactors = F)
test = test %>% select(match_id, killer_name, player_assists, player_dist_ride,player_dist_walk,player_dmg,player_kills,player_survive_time,killer_placement)

test$top10_or_not <- ifelse(test$killer_placement>10, 0, 1)
test = unique(test)

test = test %>% select(player_assists, player_dist_ride,player_dist_walk,player_dmg,player_kills,player_survive_time,top10_or_not)
```



## downsampling data
```{r}
library(caret,warn.conflicts = F)
set.seed(1000)
train$top10_or_not=as.factor(train$top10_or_not)
downSampledMiramarSolo1 <- downSample(x = train[, -ncol(train)], y = train$top10_or_not)
table(downSampledMiramarSolo1$Class)
filteredSolo1 = downSampledMiramarSolo1
```


## Logistic Regression
```{r}
mylogit1 <- suppressWarnings(glm(Class ~ . , data = filteredSolo1, family=binomial(link="logit")))
summary(mylogit1)
```



## Logistic Regression
```{r}

# training accuracy
predValidtrain1 = predict(mylogit1, newdata = filteredSolo1, type = "response")
glm.predtrain1 = ifelse(predValidtrain1 > 0.50, 1, 0)
print("classification rate: train")
mean(glm.predtrain1 == filteredSolo1$Class)

# test accuracy
test$top10_or_not=as.factor(test$top10_or_not)
predValid1 = predict(mylogit1, newdata = test, type = "response")
glm.pred1 = ifelse(predValid1 > 0.50, 1, 0)
print("classification rate: test")
mean(glm.pred1 == test$top10_or_not)

# f1 score: test
y1 <- factor(glm.pred1)
predictions1 <- factor(test$top10_or_not)
precision1 <- posPredValue(predictions1, y1, positive="1")
recall1 <- sensitivity(predictions1, y1, positive="1")
F1_score <- (2 * precision1 * recall1) / (precision1 + recall1)
print("F1 Score: test")
F1_score


```

## correlation matrix
```{r}
train_2 <- train
names(train_2)[1] <- "Assists"
names(train_2)[2] <- "Distance.Ride"
names(train_2)[3] <- "Distance.Walk"
names(train_2)[4] <- "Damage"
names(train_2)[5] <- "Kills"
names(train_2)[6] <- "Survive.Time"
library(GGally,warn.conflicts = F)
suppressWarnings(ggcorr(train_2, palette = "RdBu", label = TRUE))
```



## removing multicollinearity
```{r}
colSums(is.na(filteredSolo1))
train_mod <- filteredSolo1[,-c(4,6)]
test_mod <- test[,-c(4,6)]
print("modified cols")
colSums(is.na(train_mod))
```


## logistic on modified data
```{r}

mylogit2 <- glm(Class ~ . , data = train_mod, family=binomial(link="logit"))
summary(mylogit2)
```



# results
```{r}
#training accuracy
predValidtrain2 = predict(mylogit2, newdata = train_mod, type = "response")
glm.train2 = ifelse(predValidtrain2 > 0.50, 1, 0)
print("classification rate: train")
mean(glm.train2 == train_mod$Class)

#test accuracy
test_mod$top10_or_not=as.factor(test_mod$top10_or_not)
predValid2 = predict(mylogit2, newdata = test_mod, type = "response")
glm.pred2 = ifelse(predValid2 > 0.50, 1, 0)
print("classification rate: train")
mean(glm.pred2 == test_mod$top10_or_not)

# f1 score on test
y2 <- factor(glm.pred2)
predictions2 <- factor(test_mod$top10_or_not)
precision2 <- posPredValue(predictions2, y2, positive="1")
recall2 <- sensitivity(predictions2, y2, positive="1")
F1_score2 <- (2 * precision2 * recall2) / (precision2 + recall2)
print("F1 score: test")
F1_score2


```

## Logistic Regression:

# Individual:

```{r}
newTestLogit = test_mod
newTestLogit$pred <- predict(mylogit2, test_mod, type = "response")
ggplot(newTestLogit, aes(x=player_kills, y=pred, color = top10_or_not)) + geom_point(alpha = 0.25) + annotate("text", label = "Predicted that player lies in top 10", x = 20, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 20, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs Number of Kills") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Logistic Regression Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Number of Kills") 
```

```{r}
ggplot(newTestLogit, aes(x=player_dist_walk, y=pred, color = top10_or_not)) + geom_point(size = 0.05) + annotate("text", label = "Predicted that player lies in top 10", x = 9000, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 9000, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs Total Distance Walked") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Logistic Regression Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Distance Walked") 
```

```{r}
ggplot(newTestLogit, aes(x=player_dist_ride, y=pred, color = top10_or_not)) + geom_point(size = 0.05) + annotate("text", label = "Predicted that player lies in top 10", x = 17500, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 17500, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs Total Distance Ridden") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Logistic Regression Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Distance Ridden") 

```

```{r}
ggplot(newTestLogit, aes(x=player_assists, y=pred, color = top10_or_not)) + geom_point(size = 0.05) + annotate("text", label = "Predicted that player lies in top 10", x = 3, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 3, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs Player Assists") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Logistic Regression Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Player Assists") 

```

Interactions:

```{r}
ggplot(newTestLogit, aes(x=player_kills * player_dist_walk, y=pred, color = top10_or_not)) + geom_point(alpha = 0.25) + annotate("text", label = "Predicted that player lies in top 10", x = 75000, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 75000, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs (Kills * Distance Walked)") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Logistic Regression Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Kills * Distance Walked") 
```

```{r}
ggplot(newTestLogit, aes(x=player_dist_ride * player_dist_walk, y=pred, color = top10_or_not)) + geom_point(alpha = 0.25) + annotate("text", label = "Predicted that player lies in top 10", x = 40000000, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 40000000, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs (Distance Ridden * Distance Walked)") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Logistic Regression Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Distance Ridden * Distance Walked")
```

```{r}
library(party,warn.conflicts = F)
library(randomForest,warn.conflicts = F)

random_forest_model <- randomForest(Class ~ . , data = train_mod)

print(random_forest_model) 

predtrain <- predict(random_forest_model, train_mod, type = "class")
print("classification rate: train")
mean(predtrain == train_mod$Class)

print("classification rate: test")
test_mod$top10_or_not=as.factor(test_mod$top10_or_not)
predRF <- suppressWarnings(predict(random_forest_model, test_mod, type = "class"))
suppressWarnings(mean(predRF == test_mod$top10_or_not))

library(caret,warn.conflicts = F)
y <- predRF
predictions <- suppressWarnings(train_mod$Class)
precision <- suppressWarnings(posPredValue(predictions, y, positive="1"))
recall <- suppressWarnings(sensitivity(predictions, y, positive="1"))
F1 <- (2 * precision * recall) / (precision + recall)
print("F1 score: test")
F1

suppressWarnings(varImpPlot(random_forest_model)) 
suppressWarnings(importance(random_forest_model))
```

Random Forest:

```{r}
newTestRF = test_mod
newTestRF$pred <- predict(random_forest_model, test_mod, type = "prob")[,2]
ggplot(newTestRF, aes(x=player_kills, y=pred, color = top10_or_not)) + geom_point(alpha = 0.25) + annotate("text", label = "Predicted that player lies in top 10", x = 20, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 20, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs Number of Kills") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Random Forest Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Number of Kills") 
```

```{r}
ggplot(newTestRF, aes(x=player_dist_walk, y=pred, color = top10_or_not)) + geom_point(size = 0.05) + annotate("text", label = "Predicted that player lies in top 10", x = 9000, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 9000, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs Total Distance Walked") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Random Forest Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Distance Walked") 
```

```{r}
ggplot(newTestRF, aes(x=player_dist_ride, y=pred, color = top10_or_not)) + geom_point(size = 0.05) + annotate("text", label = "Predicted that player lies in top 10", x = 17500, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 17500, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs Total Distance Ridden") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Random Forest Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Distance Ridden") 

```

```{r}
ggplot(newTestRF, aes(x=player_assists, y=pred, color = top10_or_not)) + geom_point(size = 0.05) + annotate("text", label = "Predicted that player lies in top 10", x = 3, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 3, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs Player Assists") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Random Forest Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Player Assists") 

```

Interactions:

```{r}
ggplot(newTestRF, aes(x=player_kills * player_dist_walk, y=pred, color = top10_or_not)) + geom_point(alpha = 0.25) + annotate("text", label = "Predicted that player lies in top 10", x = 75000, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 75000, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs (Kills * Distance Walked)") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Random Forest Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Kills * Distance Walked") 
```

```{r}
ggplot(newTestRF, aes(x=player_dist_ride * player_dist_walk, y=pred, color = top10_or_not)) + geom_point(alpha = 0.25) + annotate("text", label = "Predicted that player lies in top 10", x = 40000000, y = 0.75, size = 2.5, colour = "black") + geom_hline(yintercept = 0.5, color = "black",linetype = "dashed") + annotate("text", label = "Predicted that player does not lie in top 10", x = 40000000, y = 0.25, size = 2.5, colour = "black") + theme_bw() + ggtitle("Player's Position in the Top 10 vs (Distance Ridden * Distance Walked)") + 
theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) + labs(subtitle = '(Using the Random Forest Model)',color='Top 10 flag (Actual)') + theme(legend.box.background = element_rect(colour = "black")) + ylab("Predicted Probability") + xlab("Distance Ridden * Distance Walked")
```

